Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-22 talk_ucl_cdt_200622/adaptive.tex
update typesetting in the toy theory slide
Adaptive phrasing changes, validation set

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Two evaluation sets:
		\begin{itemize}
		    \item Adaptively-sampled dataset
		    \item Independent random dataset
		\end{itemize}
		\vspace{15pt}

		Placebo comparison -- a baseline scheme without MCMC, incremental uniform-random samples.

		\column{0.4\paperwidth}
		\includegraphics[width=0.4\paperwidth]{sintoy}

@@

    $60\%$ decrease in MAE for independent evaluation (dashed) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy

>>>>

	\vspace{-1em}
	{\footnotesize
		\hfill(where $C$~enumerates all continuous variables)
	}

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Evaluation set:
		\begin{itemize}
		    \item Adaptive samples
		    \item Generated during runtime
		\end{itemize}
		Validation set:
		\begin{itemize}
		    \item Uniform random samples
		    \item Generated independently
		\end{itemize}
		\vspace{15pt}

		Placebo comparison -- incremental uniform-random samples, no MCMC.

		\column{0.4\paperwidth}
		\hspace{-20pt}\includegraphics[width=0.45\paperwidth]{sintoy}

@@

    $60\%$ decrease in MAE for validation set (dashed) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy
